### 2014-01-15 manuscripts/dpp-msbayes/dpp-msbayes.tex
Working on dpp manuscript.
Proofreading and incorporating edits throughout the manuscript.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent To understand the processes that generate biodiversity, it is
    important to account for large-scale processes that affect the evolutionary
    history of groups of co-distributed populations of organisms.
    Such events predict temporally clustered divergences times, a pattern
    that can be estimated from genetic data from co-distributed species.
    We introduce a new approximate-Bayesian model for comparative
    phylogeographical model-choice that estimates the temporal distribution of
    divergences across taxa from multi-locus DNA sequence data.
    Our model is an extension of the model implemented in \msb.
    By reparameterizing the model, and using more flexible priors on divergence
    models and nuisance parameters, we improve the robustness, accuracy, and power
    of the method for estimating the posterior probabilities of models
    of divergence across taxa.
    Our results demonstrate that the bias of the \msb model toward inferring
    models of clustered divergences is caused by a combination of (1) uniform
    priors on nuisance parameters hindering the marginal likelihoods of models
    with more divergence time parameters, and (2) a prior on divergence models
    that disfavors models with intermediate numbers of divergence time
    parameters.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent To understand the processes that generate biodiversity, it is
    important to account for large-scale processes that affect the evolutionary
    history of groups of co-distributed populations of organisms.
    Such events predict temporally clustered divergences times, a pattern
    that can be estimated using genetic data from co-distributed species.
    We introduce a new approximate-Bayesian model for comparative
    phylogeographical model-choice that estimates the temporal distribution of
    divergences across taxa from multi-locus DNA sequence data.
    Our model is an extension of that implemented in \msb.
    By reparameterizing the model, introducing more flexible priors on
    demographic and divergence-time parameters, and implementing a
    non-parametric Dirichlet-process prior over divergence models, we improve
    the robustness, accuracy, and power of the method for estimating shared
    evolutionary history across taxa.
    Our results demonstrate that the tendency of the \msb model to spuriously
    support models of clustered divergences is caused by a combination of (1)
    uniform priors on nuisance parameters hindering the marginal likelihoods of
    models with more divergence-time parameters, and (2) a prior on divergence
    models that disfavors models with intermediate numbers of divergence-time
    parameters.
    The new method addresses both of these issues and yields more robust
    estimates of posterior uncertainty, and thus greatly reduces the tendency
    of the model to incorrectly estimate biogeographically interesting models
    with strong support.
